Who Needs Privacy?

### 2019-02-12 manuscript/archive/manuscript_2019-02-07.RmD
- Major changes regarding everything: analyses (e.g., inclusion of bifactor models), ms, etc.

(ref:abstract)
In this study we analyzes how personality relates to peoples' need for privacy. For example, we analyze if the so-called "nothing-to-hide" argument is correct: Do people who lack integrity really desire more privacy? Moreover, we also analyze the relation between need for privacy and sociability, anxiety, risk aversion, and traditionality.
Using an online questionnaire with _N_ = `r n_d` mostly student respondents, we found that it is possible to predict a considerable part of peoples' need for privacy on the basis of their personalities. For example, we indeed found that repondents who reported less integrity than others also desired more anonymity. Moreover, more traditional and more anxious respondents desired more privacy from the government, while more risk averse and less sociable respondents desired more privacy from other people.

@@

```{r need-for-privacy-items}
kable(t_pri_nee, "latex", booktabs = TRUE, linesep = "",
      caption = "Overview of the Items Measuring the Need for Privacy") %>% 
  column_spec(3, width = "10cm") %>% 
  kable_styling(latex_options="scale_down", font_size = 7)
```

@@

This study analyzed how the need for privacy can be predicted by means of personality. In a study with `r n_d` students from a large US university, we measured the need for privacy with 22 items. Fifteen items formed a well-fitting bifactor model, with one factor measuring the general desire for privacy, and three specific factors measuring the need for privacy from the government, the need for privacy from other people, and the need for anonymity. The factor solution we found is in line with privacy theory, which subsumes a vertical level (here, privacy from the government) and a horizontal level (here, privacy from other people). The third dimension, need for anonymity, can be argued to exist on the diagonal, as one can be anonymous both from the government and from other people.

>>>>

(ref:abstract)
The logic underpinning the so-called “nothing-to-hide” argument in the privacy literature posits that people who lack integrity desire more privacy. This study analyzes how integrity and, in addition, four other personality traits relate to peoples’ need for privacy along three dimensions: (a) need for anonymity, (b) need for privacy from other individuals, and (b) need for privacy from government surveillance. Specifically, we analyze the relation between need for privacy and integrity, sociability, anxiety, risk aversion, and traditionality. Using an online questionnaire with `r n_d` student respondents, we found that it is possible to predict a considerable part of peoples’ need for privacy on the basis of personality. For example, we indeed found that respondents who reported less integrity desired more anonymity. Moreover, more traditional and more anxious respondents desired more privacy from the government, while more risk averse and less sociable respondents desired more privacy from other people.

@@

```{r need-for-privacy-items}
d_t_items <- rbind(
  t_pri_nee %>% filter(name %in% pri_nee_gov_items),
  t_pri_nee %>% filter(name %in% pri_nee_int_items),
  t_pri_nee %>% filter(name %in% pri_nee_ano_items)) %>% 
  select(content)
kable(d_t_items, "latex", booktabs = TRUE, linesep = "",
      caption = "Overview of the Items Measuring Need for Privacy") %>% 
  # column_spec(3, width = "10cm") %>% 
  kable_styling(latex_options="scale_down", font_size = 10) %>% 
  group_rows("Privacy need government", 1, 5) %>%
  group_rows("Privacy need interpersonal", 6, 9) %>%
  group_rows("Privacy need anonymity", 10, 13)
```

@@

This study analyzed how the need for privacy can be predicted by means of personality. In a study with `r n_d` students from a large US university, we measured the need for privacy with 22 items. Fifteen items formed a well-fitting bifactor model, with one factor measuring the general need for privacy, and three specific factors measuring the need for privacy from the government, the need for privacy from other people, and the need for anonymity. The factor solution we found is in line with privacy theory, which subsumes a vertical level (here, privacy from the government) and a horizontal level (here, privacy from other people). The third dimension, need for anonymity, can be argued to exist on the diagonal, as one can be anonymous both from the government and from other people.

### 2019-02-12 manuscript/archive/manuscript_2019-02-08.RmD
- Major changes regarding everything: analyses (e.g., inclusion of bifactor models), ms, etc.

author: 
  - name          : "Tobias Dienlin"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "University of Hohenheim, Department of Media Psychology (540F)"
    email         : "tobias.dienlin@uni-hohenheim.de"
  - name          : "Miriam Metzger"
    affiliation   : "1,2"

@@

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract          : (ref:abstract)
keywords          : "Privacy, personality, anonymity, integrity, SEM"

@@

```{r setup, include = FALSE}
devtools::install_git("https://github.com/tdienlin/td")
packages <- c("devtools", "ggplot2", "kableExtra", "lavaan", "magrittr", 
              "papaja", "semPlot", "td")
lapply(packages, library, character.only = TRUE)
load("../data/workspace.RData")
```

(ref:abstract)
The logic underpinning the so-called “nothing-to-hide” argument in the privacy literature posits that people who lack integrity desire more privacy. This study analyzes how integrity and, in addition, four other personality traits relate to peoples’ need for privacy along three dimensions: (a) need for anonymity, (b) need for privacy from other individuals, and (b) need for privacy from government surveillance. Specifically, we analyze the relation between need for privacy and integrity, sociability, anxiety, risk aversion, and traditionality. Using an online questionnaire with `r n_d` student respondents, we found that it is possible to predict a considerable part of peoples’ need for privacy on the basis of personality. For example, we indeed found that respondents who reported less integrity desired more anonymity. Moreover, more traditional and more anxious respondents desired more privacy from the government, while more risk averse and less sociable respondents desired more privacy from other people.

With this study, we want to answer the following question. Why do people desire privacy? To date there is only little research on why people desire privacy and how the need for privacy can be predicted by aspects of personality. Why do some people not care whether government agencies such as the NSA are collecting their data [@Greenwald.2013], and why do others protest vehemently in order to protect their privacy?

We think that finding an answer to this question is important: Given that government agencies are collecting large amounts of data hoping to reduce criminality and terrorism, and given that government agencies are collecting this data preemptively and without concrete suspicions, it seems relevant to find out whether this practice of mass surveillance can be justified based on the nothing-to-hide argument. As a result, the main question of this paper is: Do people who desire more privacy really have more to hide and, more generally, what are personality facets that determine peoples' overall need for privacy?

@@

```{r psychometrics, results="asis"}
apa_table(t_psyc, font_size = "footnotesize",
          caption="Psychometrics of Variables Used.",
          note = "All items were measured on 7-point scales with Likert response options. Alpha = Cronbach's alpha (internal consistency); omega = Raykov's omega (composite reliability); ave = average variance extracted."
          )
```

@@

Exploratory and confirmatory factor analyses finally revealed a well-fitting bifactor model, which consisted of one general factor measuring a general need for privacy and three specific ones measuring the need for privacy from the government, the need for privacy from other people, and the need for anonymity. For a list of all items, see Table \@ref(tab:need-for-privacy-items). For an overview of the items' loadings in the final bifactor model, see Figure \@ref(fig:need-for-privacy-loadings).

```{r need-for-privacy-loadings, fig.cap="Overview of the bifactor model for the need for privacy"}
plot(p_pri_nee)
```

@@

```{r need-for-privacy-items}
d_t_items <- rbind(
  t_pri_nee %>% filter(name %in% pri_nee_gov_items),
  t_pri_nee %>% filter(name %in% pri_nee_int_items),
  t_pri_nee %>% filter(name %in% pri_nee_ano_items)) %>% 
  select(content)
kable(d_t_items, "latex", booktabs = TRUE, linesep = "",
      caption = "Overview of the Items Measuring Need for Privacy") %>% 
  # column_spec(3, width = "10cm") %>% 
  kable_styling(latex_options="scale_down", font_size = 10) %>% 
  group_rows("Privacy need government", 1, 5) %>%
  group_rows("Privacy need interpersonal", 6, 9) %>%
  group_rows("Privacy need anonymity", 10, 13)
```

@@

```{r results, results="asis"}
apa_table(dplyr::select(t_results, -Outcome),
          font_size = "scriptsize",
          align = c("l", rep("r", 5)), 
          stub_indents = list("Privacy need general" = c(1:8),
                              "Privcacy need government" = c(9:16),
                              "Privacy need interpersonal" = c(17:24),
                              "Privacy need anonymity" = c(25:32)),
          caption = "Results of the main factorial model."
)
```

```{r results-factor, fig.cap="Overview of results. Shows the 95% confidence intervals of standardized coefficients.", fig.height=3}
plot(p_main)
```

To begin with, we found that the final model we estimated to test our hypotheses fit the data moderately well, `r fit_txt(main_fit, scaled = TRUE)`. Our first hypothesis stated that people reporting more integrity than others would need less privacy. Indeed, the results showed that respondents who reported more integrity than others desired moderately less anonymity. The relation with general privacy showed the same relation; however, it was marginally not significant. Interestingly, respondents who reported more integrity desired _more_ privacy from other people. No significant relation with the need for privacy from the government was found.

@@

In sum, the predictors could explained `r inspect(main_fit, 'r2')["pri_nee_gen"] * 100 %>% round(0)`% of the variance in the general need for privacy, `r inspect(main_fit, 'r2')["pri_nee_gov"] * 100 %>% round(0)`% of the variance in the need for privacy from the government, `r inspect(main_fit, 'r2')["pri_nee_int"] * 100 %>% round(0)`% of the variance in the need for privacy from other people, and `r inspect(main_fit, 'r2')["pri_nee_ano"] * 100 %>% round(0)`% of the variance in the need for anonymity.

@@

```{r results-items, fig.cap="Overview of results. Shows the 95% confidence intervals of standardized coefficients."}
plot(p_main_items)
```

@@

This study analyzed how the need for privacy can be predicted by means of personality. In a study with `r n_d` students from a large US university, we measured the need for privacy with 22 items. Fifteen items formed a well-fitting bifactor model, with one factor measuring the general need for privacy, and three specific factors measuring the need for privacy from the government, the need for privacy from other people, and the need for anonymity. The factor solution we found is in line with privacy theory, which subsumes a vertical level (here, privacy from the government) and a horizontal level (here, privacy from other people). The third dimension, need for anonymity, can be argued to exist on the diagonal, as one can be anonymous both from the government and from other people.

@@

>>>>

author: 
  - name          : "Tobias Dienlin"
    affiliation   : "1"
    corresponding : yes
    address       : "University of Hohenheim, Department of Media Psychology (540F), 70599 Stuttgart, Germany"
    email         : "tobias.dienlin@uni-hohenheim.de"
  - name          : "Miriam Metzger"
    affiliation   : "2"
    email         : "metzger@ucsb.edu"

@@

authornote: |
  Tobias Dienlin, Department of Media Psychology, University of Hohenheim, Germany; Miriam Metzger, Department of Communication, University of California, Santa Barbara, United States of America.

abstract          : (ref:abstract)
keywords          : "Privacy, need for privacy, personality, anonymity, integrity, SEM"

@@

```{r setup, include = FALSE}
devtools::install_git("https://github.com/tdienlin/td")
packages <- c("devtools", "ggplot2", "kableExtra", "lavaan", "magrittr", 
              "papaja", "semPlot", "td", "tidyverse")
lapply(packages, library, character.only = TRUE)
load("../data/workspace.RData")
```

(ref:abstract)
This study analyzes how personality traits relate to peoples’ need for privacy. We focus on three dimensions: (a) need for privacy from government surveillance, (b) need for privacy from other individuals, and (c) need for anonymity. Using an online questionnaire with `r n_d` student respondents, several relationships were found. For example, results showed that people who reported less integrity desired more anonymity. Less sociable people desired considerably more privacy on all three dimensions. While anxious people desired less privacy from government surveillance, risk avoidant people desired more privacy from other people. Traditionalism did not relate to need for privacy. Together, the results have several interesting impliciations. For example, they shed some light on the nothing-to-hide argument: A person who desires more anonymity might indeed be of less integrity. However, it is equally plausible that this person is just a little less gregarious.

Whereas some people protest the fact that government agencies such as the NSA are collecting large amounts of person-related data, others do not care [@Greenwald.2013]. Whereas some are happy to tell a friend a personal secret, others refrain from doing so. Whereas some people use pseudonyms to communicate online, again, others do not. Why do some people need more privacy than others, and how do they differ from one another?

In light of the increasing digitization of everyday life, which has led to the commodification and monetization of personal information [@Sevignani.2017], privacy has become one of the most important topics of the day. To date, however, we still know suprisingly little about who needs privacy and who does not, and how the need for privacy can be predicted by aspects of personality. As a result, the main question of this paper is: What are personality facets that determine peoples' overall need for privacy?

@@

```{r psychometrics, results="asis"}
apa_table(t_psyc, font_size = "footnotesize",
          caption="Psychometrics of Variables Used.",
          note = "All items were measured on 7-point scales with Likert response options. Alpha = Cronbach's alpha (internal consistency); omega = Raykov's omega (composite reliability); ave = average variance extracted.",
          stub_indents = list("Privacy need" = c(1:4)))
```

@@

Exploratory and confirmatory factor analyses finally revealed a well-fitting bifactor model, which consisted of one general factor measuring a general need for privacy and three specific ones measuring the need for privacy from the government, the need for privacy from other people, and the need for anonymity. For a list of all items, see Table \@ref(tab:need-for-privacy-items).

@@

```{r need-for-privacy-items}
d_t_items <- rbind(
  t_pri_nee %>% filter(name %in% pri_nee_gov_items),
  t_pri_nee %>% filter(name %in% pri_nee_int_items),
  t_pri_nee %>% filter(name %in% pri_nee_ano_items)) %>% 
  select("Item content" = content) %>% 
  mutate_all(linebreak)
kable(d_t_items, "latex", booktabs = TRUE, linesep = "",
      caption = "Overview of Items Measuring Need for Privacy") %>% 
  # column_spec(1, width = "16cm") %>% 
  kable_styling(latex_options="scale_down") %>% 
  group_rows("Privacy need government", 1, 5) %>%
  group_rows("Privacy need interpersonal", 6, 9) %>%
  group_rows("Privacy need anonymity", 10, 13)
```

@@

```{r results, results="asis"}
apa_table(dplyr::select(t_results_threefactors, -Outcome),
          font_size = "footnotesize",
          align = c("l", rep("r", 5)), 
          stub_indents = list("Privcacy need government" = c(1:8),
                              "Privacy need interpersonal" = c(9:16),
                              "Privacy need anonymity" = c(17:24)),
          caption = "Results of the main factorial model."
)
```

```{r results-factor, fig.cap="Overview of results. Shows the 95% confidence intervals of standardized coefficients.", fig.height=3}
plot(p_results_threefactors)
```

To begin with, we found that the final model we estimated to test our hypotheses fit the data moderately well, `r fit_txt(results_threefactors_fit, scaled = TRUE)`. Our first hypothesis stated that people reporting more integrity than others would need less privacy. Indeed, the results showed that respondents who reported more integrity than others desired moderately less anonymity. The relation with general privacy showed the same relation; however, it was marginally not significant. Interestingly, respondents who reported more integrity desired _more_ privacy from other people. No significant relation with the need for privacy from the government was found.

@@

In sum, the predictors could explained `r inspect(results_threefactors_fit, 'r2')["pri_nee_gen"] * 100 %>% round(0)`% of the variance in the general need for privacy, `r inspect(results_threefactors_fit, 'r2')["pri_nee_gov"] * 100 %>% round(0)`% of the variance in the need for privacy from the government, `r inspect(results_threefactors_fit, 'r2')["pri_nee_int"] * 100 %>% round(0)`% of the variance in the need for privacy from other people, and `r inspect(results_threefactors_fit, 'r2')["pri_nee_ano"] * 100 %>% round(0)`% of the variance in the need for anonymity.

@@

@@

With this study, we want to answer the following question. Why do people desire privacy?
This study analyzed how the need for privacy can be predicted by means of personality. In a study with `r n_d` students from a large US university, we measured the need for privacy with 22 items. Fifteen items formed a well-fitting bifactor model, with one factor measuring the general need for privacy, and three specific factors measuring the need for privacy from the government, the need for privacy from other people, and the need for anonymity. The factor solution we found is in line with privacy theory, which subsumes a vertical level (here, privacy from the government) and a horizontal level (here, privacy from other people). The third dimension, need for anonymity, can be argued to exist on the diagonal, as one can be anonymous both from the government and from other people.

@@

# Contributions

- Contributed to conception and design: TD, MM
- Contributed to acquisition of data: MM
- Contributed to analysis and interpretation of data: TD, MM
- Drafted and/or revised the article: TD, MM
- Approved the submitted version for publication: TD, MM

# Funding Information

During the conception and data collection of the study, TD was funded by The German Academic Scholarship Foundation (German: Studienstiftung des deutschen Volkes), which financially supported TD's research stay at UCSB. During the writing of the article, TD was funded by the Volkswagen Foundation (German: Volkswagenstiftung), grant "Transformations of Privacy".

MM is funded by a regular and tenured full professorship at UCSB.

# Competing Interests

We declare no competing interests.

# Data accessibility statement

All the stimuli, presentation materials, participant data, analysis scripts, and a reproducible version of the manuscript can be found on this paper’s project page on the open science framework (https://osf.io/7ncpk/?view_only=38283fd9262646378e4ba1e19c9d707f). In addition, we invite everyone to suggest changes/improvements to the manuscript via our github (https://github.com/tdienlin/need_for_privacy/tree/master).
